---
title: "Sample code for extracting AEA RCT data"
author: "Lars Vilhuber"
date: '`r Sys.Date()`'
output: github_document
editor_options: 
  chunk_output_type: console
---

## Preliminaries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = TRUE)
```

```{r knitr_options, echo=FALSE, results="hide"}
options(width = 120)
knitr::opts_chunk$set(results = "hold")
```

I used both the stable release on [CRAN](https://cran.r-project.org/package=dataverse), and installed the latest development version from [GitHub](https://github.com/iqss/dataverse-client-r/) (both as of `r Sys.Date()`). 

```{r, eval = FALSE}
# Install from CRAN
install.packages("dataverse")

# Install from GitHub
# install.packages("remotes")
remotes::install_github("iqss/dataverse-client-r")
```

See the documentation on how to record the `DATAVERSE_KEY`. You can set the API Token (or key) **when logged in** at [https://dataverse.harvard.edu/dataverseuser.xhtml?selectTab=apiTokenTab](https://dataverse.harvard.edu/dataverseuser.xhtml?selectTab=apiTokenTab).

```{r knitr_options2, echo=TRUE, results="show"}
Sys.setenv("DATAVERSE_SERVER" = "dataverse.harvard.edu")
```

I am using the Dataverse at **`r Sys.getenv("DATAVERSE_SERVER")`**. A key is included in the `.Renviron`, in the prescribed format:

``` r
DATAVERSE_KEY="examplekey12345"
```

## Finding the data

```{r, eval = TRUE, echo = TRUE}
library("dataverse")
library("tidyverse")
# we need the short name for the AEA RCT dataverse
rct.repo.name <- "aearegistry"
```

Let's first get all the records:


```{r, eval = TRUE, echo = TRUE}
rct.dv <- get_dataverse(rct.repo.name)
rct.dv.contents <- dataverse_contents(rct.dv)
```

The resulting data is a list of `r length(rct.dv.contents)` elements:

```{r,  eval = TRUE, echo = FALSE}
for (i in 1:3) { print(rct.dv.contents[[i]])}
```

We will get them all, read in the list of data files, and keep those that have "trials.csv" file (and for some earlier ones, a variation on that name):

```{r, eval = TRUE, echo = TRUE}
rct.files <- tibble()
for (i in rct.dv.contents ) {
  tmp <- as_tibble(get_dataset(i)$files) %>%
    filter(originalFileFormat == "text/csv") %>%
    filter(str_detect(originalFileName,"trials") | str_detect(originalFileName,"Registry_Trials"))
  # for some reason, more recent deposits do not have the DOI in the files content
  if ( tmp$pidURL == "" ) { tmp$pidURL <- as.character(i$persistentUrl)}
  rct.files <- bind_rows(rct.files,tmp)
}
```

with variable names

```{r, eval = TRUE, echo = TRUE}
names(rct.files)
```

and contents

```{r, eval = TRUE, echo = TRUE}
head(rct.files)
```

This is to ensure we don't keep any codebooks or auxiliary files.

If we simply want to keep the latest, let's do so:

```{r, eval = TRUE, echo = TRUE}
rct.files %>% 
  filter(creationDate == max(creationDate)) %>%
  select(label,id,persistentId,pidURL,filename,originalFileName,creationDate) -> rct.latest
```

We should remember to keep track of when, since "latest" changes over time:

- AEA Registry Data used here as of `r rct.latest$creationDate`
- DOI `r rct.latest$pidURL`.

We should also cite it appropriately (not done here).

We could also use the `creationDate` or the name of the deposit to filter on a particular version (identified by a unique DOI). 

## Loading the data

We can now simply load the file by DOI or by `id`:

```{r, eval = TRUE, echo = TRUE}
rct.data.raw <- get_dataframe_by_id(fileid=rct.latest$id[1],.f = readr::read_csv,original = TRUE)

head(rct.data.raw %>% select(RCT_ID,Title,`Last update date`))

```

